---
title: "Tests fonctions ASPIRE 2020"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

Tests des différentes fonctions du package `ASPIRE` :
```{r}
library(ASPIRE)
```

## Fonction `Transf_ASPIRE`:

Les valeurs pour tester :

```{r}
VAL_tests <- seq(from = -4, to = 16, by = 1)
VAL_MEAN_REF_tests <- 6
XVAL_tests <- c(1, 6, 10)
YSCO_tests <- c(0, 1, 0.5)

Transf_ASPIRE(VAL = VAL_tests, UTIL = "continuous",VAL_MEAN_REF = VAL_MEAN_REF_tests)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "continuous",VAL_MEAN_REF = VAL_MEAN_REF_tests, NEG = TRUE)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "threshold",VAL_MEAN_REF = VAL_MEAN_REF_tests)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "thresholdalpha",VAL_MEAN_REF = VAL_MEAN_REF_tests,ALPHA = 4)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "hump",VAL_MEAN_REF = VAL_MEAN_REF_tests)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "step",VAL_MEAN_REF = VAL_MEAN_REF_tests)
Transf_ASPIRE(VAL = VAL_tests, UTIL = "perso",VAL_MEAN_REF = VAL_MEAN_REF_tests,XVAL = XVAL_tests, YSCO = YSCO_tests)
```

```{r}
VAL_tests <- seq(from = -4, to = 16, by = 0.01)
VAL_MEAN_REF_tests <- 6
ALPHA_tests <- 4
XVAL_tests <- c(1, 6, 10)
YSCO_tests <- c(0, 1, 0.5)
```

Vérifier que ça marche bien pour toutes les valeurs de `UTIL` :

```{r}
UTIL_tests_FR <- c("continu" ,"seuil" , "seuilalpha","bosse","perso","pas" ,"pasalpha" ,"paspperso")
UTIL_tests_EN <- c("continuous","threshold","thresholdalpha","hump" ,"perso","step","stepalpha","stepperso")

par(mfrow=c(2,4))

for (i in UTIL_tests_FR)
{
VAL_transf_test <- Transf_ASPIRE(VAL = VAL_tests, UTIL = i, VAL_MEAN_REF = VAL_MEAN_REF_tests, ALPHA = ALPHA_tests, XVAL = XVAL_tests, YSCO = YSCO_tests)
plot(VAL_tests, VAL_transf_test, type="l",lwd = 2, col = 2, ylim = c(-1,3), bty="n", main = i)
abline(v = VAL_MEAN_REF_tests, lty = 2)
abline(h = 0, col = "grey50") ; abline(v = 0, col = "grey50") 
}

for (i in UTIL_tests_EN)
{
VAL_transf_test <- Transf_ASPIRE(VAL = VAL_tests, UTIL = i, VAL_MEAN_REF = VAL_MEAN_REF_tests, ALPHA = ALPHA_tests, XVAL = XVAL_tests, YSCO = YSCO_tests)
plot(VAL_tests, VAL_transf_test, type="l",lwd = 2, col = 2, ylim = c(-1,3), bty="n", main = i)
abline(v = VAL_MEAN_REF_tests, lty = 2)
abline(h = 0, col = "grey50") ; abline(v = 0, col = "grey50") 
}

par(mfrow=c(1,1))

```

## Fonction `Variable`:

```{r}
# ASPIRE.var is a data.frame included in the ASPIRE package
Var1 <- Variable(values = ASPIRE.var$Div_Butterflies,
         ref = ASPIRE.var$Div_Butterflies_Ref,
         utility = "continuous")
```

## Fonction `Var.barplot`:

```{r fig.height=4, fig.width=5}
par(mfrow=c(1,2))

Var.barplot(variab = Var1)
Var.barplot(variab = Var1, plot.ref = FALSE, 
            ylim = c(0,25),transf = TRUE, col = "cadetblue")
```

## Fonction `Objective`:

```{r}
# ASPIRE.var and ASPIRE.obj are data.frame included in the ASPIRE package
# creation of the different Variable objects:
for(i in 1:nrow(ASPIRE.obj))
{
  eval(parse(text = paste(names(ASPIRE.var)[i],
                          "<-Variable(values = ASPIRE.var[,i],ref = ASPIRE.var[,i+(ncol(ASPIRE.var)/2)],utility = ASPIRE.obj$Utility[i])")))
}
# creation of an Objective object:
Obj1 <- Objective(var_names = c("Div_Butterflies","Div_Plant","Compo_Butterflies","Compo_Plant"),
                  var_weight = c(2,1,1,2))
```

## Fonction `Obj.barplot`:

```{r fig.height=4, fig.width=5}
# plot:
Obj.barplot(obj = Obj1)
Obj.barplot(obj = Obj1,plot.ref = FALSE, ylim = c(0,2), col = "cadetblue",las.x = 2, cex.x = 0.7)
```

## Fonction `Obj.radar.plot`:

```{r fig.height=4, fig.width=5}
# plot:
Obj.radar.plot(obj = Obj1)
Obj.radar.plot(obj = Obj1,limited = FALSE, transp = 0.1,
               col = "c3",main = "Nice title",plot.ref = FALSE,vlcex=0.7)
```


## Fonction `Project`:

```{r}
# ASPIRE.var, ASPIRE.obj and ASPIRE.proj are data.frame included in the ASPIRE package
# creation of the different Variable objects:
for(i in 1:nrow(ASPIRE.obj))
{
  eval(parse(text = paste(names(ASPIRE.var)[i],
                          "<-Variable(values = ASPIRE.var[,i],ref = ASPIRE.var[,i+(ncol(ASPIRE.var)/2)],utility = ASPIRE.obj$Utility[i])")))
}
# creation of the different Objective objects
for(i in 1:(ncol(ASPIRE.obj)-2))
{
  eval(parse(text = paste(names(ASPIRE.obj)[2+i],"<-Objective(var_names = as.vector(ASPIRE.obj$Variables[ASPIRE.obj[2+i]!=0]),var_weight = ASPIRE.obj[ASPIRE.obj[2+i]!=0,2+i])")))
}
# creation of a Project object:
Proj <- Project(obj_name = c("Biodiversity","Functioning","Production"),
                stakeholders = c("Naturalist_Asso","Env_Managers","Farmers"),
                obj_weight = data.frame(c(6,3,1),c(2,2,1),c(1,1,3)))
```

## Fonction `ASPIRE_all`:

```{r}
# ASPIRE.var, ASPIRE.obj and ASPIRE.proj are data.frame included in the ASPIRE package
# creation of an ASPIRE_all object:
Proj_all <- ASPIRE_all(variable_df = ASPIRE.var,objective_df = ASPIRE.obj,project_df = ASPIRE.proj)
```

## Fonction `Var.barplot.all`:

```{r fig.height=4, fig.width=5}
par(mfrow = c(1,2))

Var.barplot.all(variable_name = "Soil_Resp", project_all = Proj_all)
Var.barplot.all(variable_name = "Soil_Resp", project_all = Proj_all, 
                main = "Soil respiration", col="cadetblue", plot.ref = FALSE, ylim=c(0,2))
```

## Fonction `Obj.barplot.all`:

```{r fig.height=5}
par(mfrow = c(1,2))

Obj.barplot.all(objective_name = "Functioning",project_all = Proj_all)
Obj.barplot.all(objective_name = "Functioning",project_all = Proj_all,
                plot.ref = FALSE,ylim = c(0,2),las.x = 2,cex.x = 0.6,main = "Birds")
```

## Fonction `Proj.obj.barplot`:

```{r}
par(mfrow=c(1,2))

Proj.obj.barplot(proj = Proj_all)
Proj.obj.barplot(proj = Proj_all, ylim = c(0,2), las.x = 2, cex.x = 0.8)
```

## Fonction `Proj.stak.barplot`:

```{r}
par(mfrow=c(1,2))

Proj.stak.barplot(proj = Proj_all)
Proj.stak.barplot(proj = Proj_all, ylim = c(0,2), las.x = 2, cex.x = 0.8)
```

## Fonction `Proj.complete.barplot`:

```{r fig.height=8}
Proj.complete.barplot(proj = Proj_all)
Proj.complete.barplot(proj = Proj_all, plot.ref = FALSE, col.stak = "cadetblue",
                      col.obj = "firebrick", col="orange", las.x = 2, cex.x = 0.7)
```

## Fonction `Proj.radar.plot`:

```{r }
par(mfrow=c(1,2))

Proj.radar.plot(proj = Proj_all)
Proj.radar.plot(proj = Proj_all, limited = FALSE, transp = 0.1,
                col = "c3", main = "Nice title", vlcex=0.7)
```

## Fonction `Proj.all.radar.plot`:

```{r }
Proj.all.radar.plot(proj = Proj_all)
Proj.all.radar.plot(proj = Proj_all, limited = FALSE, transp = 0.1,
                    col = "c3", main = "Nice title", cex.lab = 0.7)
```

```{r fig.height= 10}
Proj.all.radar.plot(proj = Proj_all, AllInOne = FALSE)
Proj.all.radar.plot(proj = Proj_all, AllInOne = FALSE, 
                    limited = FALSE, transp = 0.1,
                    col = "c3", main = "Nice title", cex.lab = 0.7)
```

## Fonction `Obj.radar.plot.all`:

```{r}
par(mfrow = c(1,2))

Obj.radar.plot.all(objective_name = "Functioning",project_all = Proj_all)
Obj.radar.plot.all(objective_name = "Functioning",project_all = Proj_all,
                   limited = FALSE,transp = 0.1,col = "c6",main = "Birds",plot.ref = FALSE)
```

## Fonction `Wheelscores`:

Exemple avec les données de McDonald et al., 2016 (Standards de la SER)

```{r fig.width=8, fig.height=8}
sousTcat<-c("Spatial mosaic","All trophic levels","All strata present",
"No undesirable species","Desirable animals","Desirable plants",
"Water chemo-physical","Substrate chemical","Substrate physical",
"Contamination","Invasive species","Over-utilization",
"Habitat links","Gene flows","Landscape flows",
"Resilience/recruitment","Habitat & interactions","Productivity/cycling")
superTcat<-c(rep(c("STRUCTURAL DIVERSITY","SPECIES COMPOSITION", "PHYSICAL CONDITIONS", 
"ABSENCE OF THREATS", "EXTERNAL EXCHANGES", "ECOSYSTEM FUNCTION"),each=3))
scoTres<-c(2,2,3,4,2,4,4,4,4,5,3,5,3,2,2,0,2,2)
Wheelscores(sousTcat,superTcat,scoTres,col.lines = "cadetblue4",col.score = "darkolivegreen2",
            col.border = "gray97",cex.sup = 1.2,cex.low = 0.9, val.max = 5)
```


## Fonction `Wheelscores.all`: 

```{r fig.width=8, fig.height=8}
Wheelscores.all(project_all = Proj_all)
Wheelscores.all(project_all = Proj_all, col.score = "cadetblue",
                col.null = 1,col.lines = "green4",col.border = "firebrick",
                cex.sup = 1.1, cex.low = 0.8, col.low = "white", col.sup = "grey95")
```
